Astrophysical calibration of gravitational-wave detectors

### 2015-07-16 docs/cosmic_cal.tex
Some changes to the prior description

The primary reason why we can use coincident observations with a GRB as a potential check of 
detector calibration is that the GRB allows us to constrain our priors on various parameters that 
would normally be highly correlated with the signal amplitude. The most important of these is that 
the GRB can provide a very tight constraint on the source distance\footnote{For \ac{BNS} and 
\ac{NSBH} systems they will be observable only in the relatively nearby Universe ($z \sim 
0.1$ and $z\sim 0.2$ for \ac{BNS} and \ac{NSBH} systems respectively), so the relation between the 
measured GRB redshift and distance is simple and our luminosity distance will be negligably 
effected by the choice of cosmology \MP{Check this?}.}. In this analysis we therefore assume that 
the source distance is known (i.e.\ has a $\delta$-function prior). Another piece of information 
that we can use from having a coincident GRB is that the system must be close to face-on, which 
allows us to place prior constraints on the system inclination angle. In our analysis we take two 
scenarios: the first use a 
prior on the beam opening angle (half-width of the beam) with a Gaussian distribution with zero mean 
and $\sigma = 5^{\circ}$, whilst the second uses $\sigma = 20^{\circ}$. Beam opening angles for 
short GRBs are relatively poorly constrained as they are based on only a few jet break detection, 
however \cite{2014ApJ...780..118F} give a median opening angle value of $\sim 10^{\circ}$. If we 
assume that the beam opening angle is a half-normal distribution, for which the median is given by 
$\sqrt{2}\erf{}^{-1}(1/2)\sigma \sim 0.67\sigma$, then a median of $\sim 10^{\circ}$ corresponds to 
$\sigma \sim 14.8^{\circ}$.

As we have assumed that the GRB progenitor is a binary neutron star system the prior we use for the 
system component masses is a Gaussian distribution for both components with means 
of $1.35\,\textrm{M}_{\odot}$ and standard deviations of $0.13\,\textrm{M}_{\odot}$ 
\MP{(reference)}. In reality, for all the systems we use in our study, the chirp mass, which 
we see from equation~\ref{eq:signal} plays a role in the overall signal amplitude, is very well 
constrained by the systems phase evolution, so our prior could be expanded with minimal effect on 
the results. In the future neutron star-black hole systems could be included, although this add the 
complication of having to include the black hole spin (by using BNS systems we have assumed that 
the spins are small enough that they will introduce only a negligible effect).

>>>>

The primary reason why we can use coincident observations with a GRB as a potential check of 
detector calibration is that the GRB allows us to constrain our priors on various parameters that 
would normally be highly correlated with the signal amplitude. The most important of these is that 
the GRB can provide a very tight constraint on the source distance\footnote{For \ac{BNS} and 
\ac{NSBH} systems they will be observable only in the relatively nearby Universe ($z \sim 
0.1$ and $z\sim 0.2$ for \ac{BNS} and \ac{NSBH} systems respectively), so the relation between the 
measured GRB redshift and distance is simple and our luminosity distance will be negligably 
effected by the choice of cosmology \MP{Check this?}.}. In this analysis we therefore assume that 
the source distance is known (i.e.\ has a $\delta$-function prior). Another piece of information 
that we can use from having a coincident GRB is that the system is likely to be relatively close to 
face-on (an therefore nearly circularly polarised), which allows us to place prior constraints on 
the system inclination angle. Beam opening angles for short GRBs are relatively poorly constrained 
as they are based on only a few jet break detections, however \cite{2014ApJ...780..118F} give a 
median opening angle value of $\sim 10^{\circ}$. If we assume that the beam opening angle is a 
half-normal distribution, for which the median is given by $\sqrt{2}\erf{}^{-1}(1/2)\sigma \sim 
0.67\sigma$, then a median of $\sim 10^{\circ}$ corresponds to $\sigma \sim 14.8^{\circ}$. We 
therefore place a Gaussian prior on the inclination angle with zero mean and $\sigma=14.8^{\circ}$.

Our prior on the system component masses is dependent on whether we are considering the source 
being a \ac{BNS} system or a \ac{NSBH}. For the former case the prior we use is a Gaussian 
distribution for both components with means of $1.35\,\textrm{M}_{\odot}$ and standard deviations 
of $0.13\,\textrm{M}_{\odot}$ \MP{(reference)}. In reality, for all the systems we use in our 
study, the chirp mass, which we see from equation~\ref{eq:signal} plays a role in the overall 
signal amplitude, is very well constrained by the systems phase evolution, so our prior could be 
expanded with minimal effect on the results. In the case of \ac{NSBH} systems we use the same 
prior as above for the neutron star, but for the black hole we use a prior based on the 
canonical masss distribution used for the rate results in \cite{2012PhRvD..85h2002A} with a mean of 
$5\,\textrm{M}_{\odot}$ and a standard deviation of $1\,\textrm{M}_{\odot}$. For the \ac{NSBH}
systems we also require a prior on the black hole spin (for \ac{BNS} systems we have assumed that 
the spins are small enough that they will be negligible). We use a uniform prior on the 
normalised aligned spin magnitude between $-1$ and $1$.
